$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-30 paper/e6ssm-tuning-paper.tex
Fixed typo we --> will

Interestingly other sensitivities are suppressed by this effect since
at the same time larger $M_3$ at higher scales reduces the soft squark
masses at $M_X$.  Therefore the stop mass contributions are
ameliorated, compared to the MSSM, both by allowing lighter stops at
$M_{SUSY}$ and by the modified RGE running.  Nonetheless the stops
still do lead to $\Delta_{m_{H_u}^2}$ increasing with the cutoff
through the usual mechanism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
  receives a positive contribution to it's mass from $m_{H_u}^2(M_X)$
  and a negative contribution from $m_{Q_3}^2(M_X)$ and
  $m_{u_3}^2(M_X)$, allowing heavy stop masses to cause fine
  tuning. In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
  cutoff increases the values of these soft masses at $M_X$ will be
  larger and there we be a bigger cancellation between them,
  increasing the sensitivity of $M_Z$ to both $m_{H_u}^2$ and the soft
  scalar masses for the stops.}.

>>>>

Interestingly other sensitivities are suppressed by this effect since
at the same time larger $M_3$ at higher scales reduces the soft squark
masses at $M_X$.  Therefore the stop mass contributions are
ameliorated, compared to the MSSM, both by allowing lighter stops at
$M_{SUSY}$ and by the modified RGE running.  Nonetheless the stops
still do lead to $\Delta_{m_{H_u}^2}$ increasing with the cutoff
through the usual mechanism \footnote{Wherein $m_{H_u}^2(M_{SUSY})$
  receives a positive contribution to it's mass from $m_{H_u}^2(M_X)$
  and a negative contribution from $m_{Q_3}^2(M_X)$ and
  $m_{u_3}^2(M_X)$, allowing heavy stop masses to cause fine
  tuning. In this case $m_{H_u}^2(M_{SUSY})$ is held fixed so as the
  cutoff increases the values of these soft masses at $M_X$ will be
  larger and there will be a bigger cancellation between them,
  increasing the sensitivity of $M_Z$ to both $m_{H_u}^2$ and the soft
  scalar masses for the stops.}.
